### 2018-08-17 sections/statistical_analysis.tex
updated bb postfit tables and added bb aux material plots

For each search, the final discriminant distributions across all analysis regions considered are jointly analysed to test for the 
presence of a signal. The statistical analysis uses a binned likelihood function ${\cal L}(\mu,\theta)$ constructed as
a product of Poisson probability terms over all bins considered in the search. This function depends
on the signal-strength parameter $\mu$, defined as a multiplicative factor to the yield for $\Hq$ signal events
normalised to a reference branching ratio $\BR_{\mathrm{ref}}(t\to Hq)=1\%$,
and $\theta$, a set of nuisance parameters that encode the effect of systematic uncertainties in the signal and background expectations. 
Therefore, the expected total number of events in a given bin depends on $\mu$ and $\theta$. 
All nuisance parameters are implemented in the likelihood function as Gaussian or log-normal constraints, with the exception of a few parameters 
that control the normalisation of the some of the background components (e.g. the \ttbin\ background in the case of the $\Hbb$ search) 
and are treated as free parameters in the fit.

@@

The test statistic $q_\mu$ is defined as the profile likelihood ratio: 
$q_\mu = -2\ln({\cal L}(\mu,{\hat{\theta}}_\mu)/{\cal L}(\hat{\mu},\hat{\theta}))$,
where $\hat{\mu}$ and $\hat{\theta}$ are the values of the parameters that
maximise the likelihood function (subject to the constraint $0\leq \hat{\mu} \leq \mu$), and ${\hat{\theta}}_\mu$ are the values of the
nuisance parameters that maximise the likelihood function for a given value of $\mu$. 
The test statistic $q_\mu$ is evaluated with the {\textsc RooFit} package~\cite{Verkerke:2003ir,RooFitManual}.
A related statistic is used to determine the probability that the observed data are compatible with the background-only hypothesis (i.e.~the discovery test)  
by setting $\mu=0$ in the profile likelihood ratio and leaving $\hat{\mu}$ unconstrained: $q_0 = -2\ln({\cal L}(0,{\hat{\theta}}_0)/{\cal L}(\hat{\mu},\hat{\theta}))$.
The $p$-value (referred to as $p_0$) representing the probability of the data being compatible with the 
background-only hypothesis is estimated by integrating
the distribution of $q_0$ obtained from background-only pseudo-experiments, approximated using the asymptotic formulae given in Refs.~\cite{Cowan:2010js}, above the observed value of $q_0$ in the data. 
%The observed $p_0$-value is checked for each explored signal scenario.
In the case of the data being compatible with the background expectation, upper limits on $\mu$, and thus on 
$\BR(t\to Hq)$, are derived by using $q_\mu$ in the CL$_{\textrm{s}}$ method~\cite{Junk:1999kv,Read:2002hq}.
For a given signal scenario, values of the $\BR(t\to Hq)$ yielding CL$_{\textrm{s}} < 0.05$, 
where CL$_{\textrm{s}}$ is computed using the asymptotic approximation~\cite{Cowan:2010js}, are excluded at $\geq 95\%$ CL.

>>>>

For each search, the final discriminant distributions across all analysis regions considered are jointly analysed to test for the 
presence of a signal. The statistical analysis uses a binned likelihood function ${\cal L}(\mu,\theta)$ constructed as
a product of Poisson probability terms over all bins considered in the search. This function depends
on the signal-strength parameter $\mu$, defined as a multiplicative factor to the yield for $\Hq$ signal events
normalised to a reference branching ratio $\BR_{\mathrm{ref}}(t\to Hq)=1\%$,
and $\theta$, a set of nuisance parameters that encode the effect of systematic uncertainties in the signal and background expectations. 
Therefore, the expected total number of events in a given bin depends on $\mu$ and $\theta$. 
All nuisance parameters are implemented in the likelihood function as Gaussian or log-normal constraints, with the exception of a few parameters 
that control the normalisation of the some of the background components (e.g. the \ttbin\ background in the case of the $\Hbb$ search), which 
are treated as free parameters in the fit.

@@

The test statistic $q_\mu$ is defined as the profile likelihood ratio: 
$q_\mu = -2\ln({\cal L}(\mu,{\hat{\theta}}_\mu)/{\cal L}(\hat{\mu},\hat{\theta}))$,
where $\hat{\mu}$ and $\hat{\theta}$ are the values of the parameters that
maximise the likelihood function (subject to the constraint $0\leq \hat{\mu} \leq \mu$), and ${\hat{\theta}}_\mu$ are the values of the
nuisance parameters that maximise the likelihood function for a given value of $\mu$. 
The test statistic $q_\mu$ is evaluated with the {\textsc RooFit} package~\cite{Verkerke:2003ir,RooFitManual}.
A related statistic is used to determine the compatibility of the observed data with the background-only hypothesis (i.e.~the discovery test)  
by setting $\mu=0$ in the profile likelihood ratio and leaving $\hat{\mu}$ unconstrained: $q_0 = -2\ln({\cal L}(0,{\hat{\theta}}_0)/{\cal L}(\hat{\mu},\hat{\theta}))$.
The $p$-value (referred to as $p_0$) representing the probability of the data being compatible with the background-only hypothesis is estimated by integrating
the distribution of $q_0$ obtained from background-only pseudo-experiments, approximated using the asymptotic formulae given in Refs.~\cite{Cowan:2010js}, 
above the observed value of $q_0$ in the data. 
%The observed $p_0$-value is checked for each explored signal scenario.
In the case of the data being compatible with the background expectation, upper limits on $\mu$, and thus on 
$\BR(t\to Hq)$, are derived by using $q_\mu$ in the CL$_{\textrm{s}}$ method~\cite{Junk:1999kv,Read:2002hq}.
For a given signal scenario, values of the $\BR(t\to Hq)$ yielding CL$_{\textrm{s}} < 0.05$, 
where CL$_{\textrm{s}}$ is computed using the asymptotic approximation~\cite{Cowan:2010js}, are excluded at $\geq 95\%$ CL.

### 2018-08-17 sections/strategy_Htautau.tex
updated bb postfit tables and added bb aux material plots

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}[t]
\begin{center}
\subfloat[]{\includegraphics[width=0.40\textwidth]{figures/Htautau/control_plots/m_tt_lephad_3j_FR.eps}}
\subfloat[]{\includegraphics[width=0.40\textwidth]{figures/Htautau/control_plots/m_tt_lephad_4j_FR.eps}} \\
\subfloat[]{\includegraphics[width=0.40\textwidth]{figures/Htautau/control_plots/ptL2_lephad_3j_FR.eps}}
\subfloat[]{\includegraphics[width=0.40\textwidth]{figures/Htautau/control_plots/ptL2_lephad_4j_FR.eps}} \\
\caption{$\Htautau$ search: Comparison between the data and background prediction for the distribution of some of the most
important BDT input variables in the $\lephad$ channel before performing the fit to data (``Pre-Fit''). The distributions are shown for
$m_{\tau\tau}^{\text{fit}}$ in (a) the ($\lephad$, 3j) region and (b) the ($\lephad$, $\geq$4j) region, and for
$p_{\text{T},2}$ in (c) the ($\lephad$, 3j)  region and (d) the ($\lephad$, $\geq$4j) region.
The contributions with real $\tauhad$ candidates from $\ttbar$,  $\ttbar V$, $\ttbar H$, and single top backgrounds are combined into
a single background source referred to as ``Top (real $\tauhad$)", whereas the small contributions from 
$Z\to \ell^+\ell^-$ ($\ell = e, \mu$) and diboson backgrounds are combined into ``Other''. 
The expected $\Hc$ signal (solid red) corresponding to $\BR(t\to Hc)=1\%$ is also shown,
added on top of the background prediction.
The last bin in all figures contains the overflow.
The bottom panel displays the ratio of data to the SM background (``Bkg'') prediction. 
The hashed area represents the total uncertainty of the background.}
\label{fig:BDT_inputs_lephad}
\end{center}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}[t]
\begin{center}
\subfloat[]{\includegraphics[width=0.40\textwidth]{figures/Htautau/control_plots/m_tt_hadhad_3j_FR.eps}}
\subfloat[]{\includegraphics[width=0.40\textwidth]{figures/Htautau/control_plots/m_tt_hadhad_4j_FR.eps}} \\
\subfloat[]{\includegraphics[width=0.40\textwidth]{figures/Htautau/control_plots/x1_fit_hadhad_3j_FR.eps}}
\subfloat[]{\includegraphics[width=0.40\textwidth]{figures/Htautau/control_plots/x2_fit_hadhad_4j_FR.eps}} \\
\caption{$\Htautau$ search: Comparison between the data and background prediction for the distribution of two of the most 
important BDT input variables in the $\hadhad$ channel before performing the fit to data (``Pre-Fit''). The distributions are shown for
$m_{\tau\tau}^{\text{fit}}$ in (a) the ($\hadhad$, 3j) region and (b) the ($\hadhad$, $\geq$4j) region, and for
(c) $x_{1}^{\text{fit}}$ in the ($\hadhad$, 3j)  region, and (d) $x_{2}^{\text{fit}}$ in the ($\hadhad$, $\geq$4j) region.
The contributions with real $\tauhad$ candidates from $\ttbar$,  $\ttbar V$, $\ttbar H$, and single top backgrounds are combined into
a single background source referred to as ``Top (real $\tauhad$)", whereas the small contributions from 
$Z\to \ell^+\ell^-$ ($\ell = e, \mu$) and diboson backgrounds are combined into ``Other''. 
The expected $\Hc$ signal (solid red) corresponding to $\BR(t\to Hc)=1\%$ is also shown,
added on top of the background prediction.
The last bin in all figures contains the overflow.
The bottom panel displays the ratio of data to the SM background (``Bkg'') prediction. 
The blue triangles indicate points that are outside the vertical range of the figure. 
The hashed area represents the total uncertainty of the background. } 
\label{fig:BDT_inputs_hadhad}
\end{center}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}[t]
\begin{center}
\subfloat[]{\includegraphics[width=0.40\textwidth]{figures/Htautau/control_plots/m_tt_lephad_3j_FR.eps}}
\subfloat[]{\includegraphics[width=0.40\textwidth]{figures/Htautau/control_plots/m_tt_lephad_4j_FR.eps}} \\
\subfloat[]{\includegraphics[width=0.40\textwidth]{figures/Htautau/control_plots/ptL2_lephad_3j_FR.eps}}
\subfloat[]{\includegraphics[width=0.40\textwidth]{figures/Htautau/control_plots/ptL2_lephad_4j_FR.eps}} \\
\caption{$\Htautau$ search: Comparison between the data and background prediction for the distribution of some of the most
important BDT input variables in the $\lephad$ channel before performing the fit to data (``Pre-Fit''). The distributions are shown for
$m_{\tau\tau}^{\text{fit}}$ in (a) the ($\lephad$, 3j) region and (b) the ($\lephad$, $\geq$4j) region, and for
$p_{\text{T},2}$ in (c) the ($\lephad$, 3j)  region and (d) the ($\lephad$, $\geq$4j) region.
The contributions with real $\tauhad$ candidates from $\ttbar$,  $\ttbar V$, $\ttbar H$, and single top backgrounds are combined into
a single background source referred to as ``Top (real $\tauhad$)", whereas the small contributions from 
$Z\to \ell^+\ell^-$ ($\ell = e, \mu$) and diboson backgrounds are combined into ``Other''. 
The expected $\Hc$ signal (solid red) corresponding to $\BR(t\to Hc)=1\%$ is also shown,
added on top of the background prediction.
The first and the last bins in all figures contain the underflow and overflow respectively.
The bottom panel displays the ratio of data to the SM background (``Bkg'') prediction.
The hashed area represents the total uncertainty on the background, excluding the normalisation uncertainty of the fake $\tauhad$ background, 
which is determined via a likelihood fit to data.}
\label{fig:BDT_inputs_lephad}
\end{center}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}[t]
\begin{center}
\subfloat[]{\includegraphics[width=0.40\textwidth]{figures/Htautau/control_plots/m_tt_hadhad_3j_FR.eps}}
\subfloat[]{\includegraphics[width=0.40\textwidth]{figures/Htautau/control_plots/m_tt_hadhad_4j_FR.eps}} \\
\subfloat[]{\includegraphics[width=0.40\textwidth]{figures/Htautau/control_plots/x1_fit_hadhad_3j_FR.eps}}
\subfloat[]{\includegraphics[width=0.40\textwidth]{figures/Htautau/control_plots/x2_fit_hadhad_4j_FR.eps}} \\
\caption{$\Htautau$ search: Comparison between the data and background prediction for the distribution of two of the most 
important BDT input variables in the $\hadhad$ channel before performing the fit to data (``Pre-Fit''). The distributions are shown for
$m_{\tau\tau}^{\text{fit}}$ in (a) the ($\hadhad$, 3j) region and (b) the ($\hadhad$, $\geq$4j) region, and for
(c) $x_{1}^{\text{fit}}$ in the ($\hadhad$, 3j)  region, and (d) $x_{2}^{\text{fit}}$ in the ($\hadhad$, $\geq$4j) region.
The contributions with real $\tauhad$ candidates from $\ttbar$,  $\ttbar V$, $\ttbar H$, and single top backgrounds are combined into
a single background source referred to as ``Top (real $\tauhad$)", whereas the small contributions from 
$Z\to \ell^+\ell^-$ ($\ell = e, \mu$) and diboson backgrounds are combined into ``Other''. 
The expected $\Hc$ signal (solid red) corresponding to $\BR(t\to Hc)=1\%$ is also shown,
added on top of the background prediction.
The first and the last bins in all figures contain the underflow and overflow respectively.
The bottom panel displays the ratio of data to the SM background (``Bkg'') prediction.
The hashed area represents the total uncertainty on the background, excluding the normalisation uncertainty of the fake $\tauhad$ background, 
which is determined via a likelihood fit to data.} 
\label{fig:BDT_inputs_hadhad}
\end{center}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
